##Analysing the data

We begin by importing all needed packages and scripts



```{r,results=FALSE, warning=FALSE,message=FALSE}
library(NMF)
library(cowplot)
library(ggplot2)
library(Seurat)
library(Matrix)
source("Clust_Graph.R")
source("heatmap.R")
source("niceDraw.R")
source("TSNE.R")
```


We also load the expression matrix. Note this matrix is already filtered and normalized to log(CPM+1).

```{r}
load("data/dat.Robj")
load("data/meta.Robj")
```

We then generate our Seurat object and move it through the standard pipeline.

```{r}
#Setup object
seur<-new("seurat",raw.data=dat)
seur<-Setup(seur,"Organoid",do.scale=F,do.center=F,do.logNormalize=F,min.genes=0,min.cells=0)

#Add metadata
seur@data.info[colnames(meta)]=meta[names(seur@ident),]

#Calculate variable genes
seur<-MeanVarPlot(seur,x.low.cutoff=1)

#Regress out covariates
seur<-RegressOut(seur,c("nGene","mito"),genes.regress=seur@var.genes)

#Run PCA
seur<-PCAFast(seur)
PCElbowPlot(seur)
```

Based on the elbowplot, we decide to use 13 pc's to perform TSNE and clustering.

```{r}
seur<-getTSNE(seur,numPC=13)
seur<-clustGraph_Seurat(seur,100,13)
TSNEPlot(seur,T)
```


This gives use the clustering we want. We can then look at marker genes to identify the clusters:

```{r}
#Marker for neurons
niceFeaturePlot(seur,"hg19_SNAP25",low="blue")

#Marker for cycling cells
niceFeaturePlot(seur,"hg19_TOP2A",low="blue")

#Marker for astrocytes
niceFeaturePlot(seur,"hg19_GFAP",low="blue")

#Neuroepithelial
niceFeaturePlot(seur,"hg19_COL1A2")

#Inhibitory Neurons
niceFeaturePlot(seur,"hg19_GAD2")

##Map cluster numbers to cell types
lst<-rep("CellType",12)
lst[c(7,10)]="Astrocytes"
lst[8]="Inhibitory Neurons"
lst[11]="Neuroepithelial"
lst[c(1,2,12)]="Neurons"
lst[c(3:6,9)]="Radial Glia"
seur@data.info["CellType"]=lst[as.numeric(as.character(seur@ident))]
```



Note that these are only come of the markers we used, see makeFigs.R for a more complete list. Note that makeFigs.R does not run, since we did not include all datsets required (due to space constraints), though they are all available from their perspective publications.


Due to size restrictions, we did not include all datasets we compared the Organoids against, only one (the Pollen dataset). 

```{r}
#Load the label used in the paper
seur<-SetAllIdent(seur,"CellType_ext")

#Load pollen data
load("data/Pollen.Robj")

#Perform analysis
COR=getCOR(seur,Pollen)
ann=data.frame(factor(rev(c(3,4,4,4,4,4))))
colnames(ann)="Lane"
COR=data.frame(COR)[,rev(c(4,5,2,1,6,3))]
COR=data.frame(COR)[c(4,2,1,3),]
aheatmap(t(COR),Rowv=seq(ncol(COR),1),Colv=seq(nrow(COR),1),annRow=ann)
```




